The Dark Matter Distribution of the Local Group inferred from Cosmological Simulations: I. The Halo Masses of M31, M33 and the Milky Way

### 2015-04-04 doc/thesis/main.tex

\documentclass{emulateapj}

\usepackage{apjfonts}
\usepackage{epsfig}
\usepackage{natbib}

@@

\citestyle{aa}
\shortauthors{Marshall et al.}
\shorttitle{The Mass of the Local Group}

@@

\author{Philip J. Marshall\altaffilmark{1}}
\author{Marc Williamson\altaffilmark{1}}
\author{Michael T. Busha\altaffilmark{2}} 
\author{Risa H. Wechsler\altaffilmark{1}}
\author{XX\altaffilmark{3}}
\author{YY\altaffilmark{4}}
\altaffiltext{1}{Kavli Institute for Particle Astrophysics and Cosmology, Stanford, CA, 94305, USA
{\tt pjm@slac.stanford.edu, rwechsler@stanford.edu}}
\altaffiltext{2}{???}
\altaffiltext{3}{XX}
\altaffiltext{4}{YY}

@@

@@

\bibliographystyle{apj}
\bibliography{references}

>>>>

\documentclass[iop,apj]{emulateapj}
\usepackage{amsmath,amssymb,amstext}

%\usepackage[breaklinks,colorlinks,citecolor=blue,linkcolor=magenta]{hyperref} 
%\renewcommand*{\sectionautorefname}{Section}
%\usepackage[all]{hypcap} %Links go to figures; breaks on deluxetables (use \capstartfalse \capstarttrue to fix it)

\usepackage{aas_macros}
\usepackage{natbib}
\bibliographystyle{apj}

\shorttitle{Short Title}
\shortauthors{Author et al.}

@@

\citestyle{aa}
\shortauthors{Williamson et al.}
\shorttitle{The Mass of the Local Group}

@@

\author{Marc Williamson\altaffilmark{1}}
\author{Philip J. Marshall\altaffilmark{1}}
\author{Michael T. Busha\altaffilmark{2}} 
\author{Risa H. Wechsler\altaffilmark{1}}

\altaffiltext{1}{Kavli Institute for Particle Astrophysics and Cosmology, Stanford, CA, 94305, USA
{\tt mwillia1@stanford.edu, pjm@slac.stanford.edu, rwechsler@stanford.edu}}
\altaffiltext{2}{???}

@@

%-----------------------------------------------------------------------------

\section{Coordinates}
\label{sec:coord}

In this section we describe the coordinate systems used in this paper and present the transformations between them.  As mentioned in the introduction, this project uses the M31 galactocentric dynamics of the MW-M31-M33 system to define a LG analog.  Specifically, we use the parameters $\distance$, $\vrad$, and $\vtan$ measured from M31 to MW and M33 respectively.  The LG analog sample is drawn using the "observed" values of these parameters.  However, the true observed values of these parameters are of course geocentric and measured in equatorial coordinates of right ascension ($\alpha$) and declination ($\delta$).  Therefore, it is necessary to be able to transform from this system to the M31 galactocentric coordinate system.  This involves many intermediate coordinate systems and transformations which will be described in the remainder of this section.
\subsection{Coordinate System Definitions}
\label{sec:c_sys_defs}
Three types of coordinate systems are used in this work: Geocentric Equatorial, Heliocentric Galactic, and Galactocentric.  Before we describe the mathematical transformations between these systems, it is important to thoroughly understand the definitions of the systems. 
\par The equatorial system is centered on the Earth and based on the concept of a celestial sphere (ie all stars are projected onto a sphere of infinite radius centered on the Earth). Two angles characterize the positions of objects on the celestial sphere: right ascension and declination. Right ascension, $\alpha$, is the angle measured eastwards along the celestial equator between the vernal equinox and the hour circle passing through an object.  Declination, $\delta$, is the angular distance of an object above or below the celestial equator.  
\par The heliocentric galactic coordinate system (often ambiguously referred to as galactic coordinates), is a different spherical coordinate system centered at the Sun.  The heliocentric fundamental plane is aligned with the galactic plane, and the primary direction is along the line connecting the sun and the galactic center.  Positions are measured in galactic latitude and longitude. Latitude, $b$, measures angular distance of an object perpendicular to the galactic plane, with positive angles to the north galactic pole. Longitude, $l$, is the angular distance measured eastward along the galactic equator from the galactic center.
\par The galactocentric coordinate system used in this paper is the same as the one used by van der Marel \citep{VdM08}.  The $Z$ axis points towards the galactic north pole, the $Y$ axis is oriented in the direction of the sun's rotation about the galactic center, and the $X$ axis points from the sun towards the galactic center. This is a standard, right-handed coordinate system.

@@

% ----------------------------------------------------------------------------
%\nocite{*}
%\bibliographystyle{unsrt}
%\bibliography{references.bib}

% ----------------------------------------------------------------------------
\nocite{*}
\bibliography{references}
